Using the ... Algorithm to Detect Kinetic Parameters of Catalytic Isomerization of the Pentane-Hexane Fraction

### 2022-09-04 2022/OPTIMA/paper.tex
all the reviewers' comments are fixed

% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%
\begin{document}
%
\title{An accelerated algorithm for finding efficient solutions in multiobjective problems with black-box multiextremal criteria\thanks{The work was supported by the Ministry of Science and Higher Education of the Russian Federation (project no.0729-2020-0055) and by the Research and Education Mathematical Center (project no. 075-02-2020-1483/1).}}
%
\titlerunning{Algorithm for finding efficient solutions in multiobjective problems}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Konstantin Barkalov\orcidID{0000-0001-5273-2471} \and
Vladimir Grishagin\orcidID{0000-0002-2884-3670} \and
Evgeny Kozinov\orcidID{0000-0001-6776-0096}}
%
\authorrunning{K. Barkalov, V. Grishagin and E. Kozinov}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia \email{\{konstantin.barkalov,evgeny.kozinov\}@itmm.unn.ru}, \email{vagris@unn.ru}}

@@

%However, the function $f(x(t))$ will not meet the Lipschitz if $f(x)$ is Lipschitzian. It will satisfy the H{\"o}lder condition
However, in the case when the function $f(x)$ is Lipschitzian this property is not valid for the reduced function. The function $f(x(t))$ will satisfy the H{\"o}lder condition
\begin{equation}\label{holder}
\left|f(x(t'))-f(x(t''))\right| \leq H \left|t'-t''\right|^{1/N}, \; t',t'' \in [0,1],
\end{equation}
with a H{\"o}lder constant $H>0$.
And if the function $f(x)$ satisfies the Lipschitz condition (\ref{lip_1}) then $H=2L\sqrt{N+3}$ (see \cite{Sergeyev2013,Strongin2000}).
As a consequence, minimization of the function $f(x(t))$  requires the use of special algorithms oriented at functions with property (\ref{holder}).

>>>>

% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%
\begin{document}
%
\title{An accelerated algorithm for finding efficient solutions in multiobjective problems with black-box multiextremal criteria\thanks{The work was supported by the Ministry of Science and Higher Education of the Russian Federation (project No. 0729-2020-0055) and by the Research and Education Mathematical Center (project No. 075-02-2020-1483/1).}}
%
\titlerunning{Algorithm for finding efficient solutions in multiobjective problems}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Konstantin Barkalov\orcidID{0000-0001-5273-2471} \and
Vladimir Grishagin\orcidID{0000-0002-2884-3670} \and
Evgeny Kozinov\orcidID{0000-0001-6776-0096}}
%
\authorrunning{K. Barkalov, V. Grishagin and E. Kozinov}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia \email{\{konstantin.barkalov,evgeny.kozinov\}@itmm.unn.ru}, \email{vagris@unn.ru}}

@@

%However, the function $f(x(t))$ will not meet the Lipschitz if $f(x)$ is Lipschitzian. It will satisfy the H{\"o}lder condition
However, in the case when the function $f(x)$ is Lipschitzian the function $f(x(t))$ will satisfy the H{\"o}lder condition
\begin{equation}\label{holder}
\left|f(x(t'))-f(x(t''))\right| \leq H \left|t'-t''\right|^{1/N}, \; t',t'' \in [0,1],
\end{equation}
with a H{\"o}lder constant $H>0$.
And if the function $f(x)$ satisfies the Lipschitz condition (\ref{lip_1}) then $H=2L\sqrt{N+3}$ (see \cite{Sergeyev2013,Strongin2000}).
As a consequence, minimization of the function $f(x(t))$  requires the use of special algorithms oriented at functions with property (\ref{holder}).

### 2022-09-04 2022/PAVT Special Issue/template.tex

In the complex problems of chemical kinetics, kinetic constants of reactions cannot be found analytically, they can only be found using numerical methods (see, for example, [references]). In this case, the quality criterion (objective function) is set in the form of a certain algorithm, which includes the stage of numerical modeling, which, in turn, makes it compute-intensive. Furthermore, in the inverse problems of chemical kinetics, the objective function can be substantially multiextremal, i.e., having many local extremes along the global one.

@@

This paper reflects the results of applying parallel methods of Lipschitz optimization developed in [refernces], to the solution of inverse problems of chemical kinetics.  
The main part of the paper is structured as follows. 
Section 2 provides a description of the mathematical model of the chemical reaction under study. Section 3 discusses the standard formulation of the Lipschitz global optimization problem and the algorithm for solving it. It also outlines the issues related to the technical aspects of the implementation of the parallel algorithm. The results of the numerical solution of the inverse problem of chemical kinetics using the developed parallel algorithm are discussed in Section 4. The last section contains the conclusion and plans for future work.

>>>>

In the complex problems of chemical kinetics, kinetic constants of reactions cannot be found analytically, they can only be found using numerical methods (see, for example, \cite{Zaynullin2020,Enikeeva2020,Koledina2019}). In this case, the quality criterion (objective function) is set in the form of a certain algorithm, which includes the stage of numerical modeling, which, in turn, makes it compute-intensive. Furthermore, in the inverse problems of chemical kinetics, the objective function can be substantially multiextremal, i.e., having many local extremes along the global one.

@@

This paper reflects the results of applying parallel methods of Lipschitz optimization developed in \cite{Barkalov2016,Strongin2018,Sysoyev2017}, to the solution of inverse problems of chemical kinetics.  
The main part of the paper is structured as follows. 
Section 2 provides a description of the mathematical model of the chemical reaction under study. Section 3 discusses the standard formulation of the Lipschitz global optimization problem and the algorithm for solving it. It also outlines the issues related to the technical aspects of the implementation of the parallel algorithm. The results of the numerical solution of the inverse problem of chemical kinetics using the developed parallel algorithm are discussed in Section 4. The last section contains the conclusion and plans for future work.
